\Title

### 2020-02-21 manuscript/manuscript.tex
Change case on acknowledgements
Remove minipage from tabular
Add manuscript (#19)
Start writing manuscript. Add BiBTeX references file. Add and/or improve
notebooks for creating schematic figures of source distributions and depth
types.

\begin{table*}
\begin{minipage}{80mm}
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source bellow data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{minipage}
\end{table*}

@@

%Describe the parameters used for each source distribution, how do we score
%each interpolation.
%Show results.

Compute the gravitational effect of the synthetic model on a regular grid of
points located at the same height.
This will be called our \emph{target grid}.
We will use it to compute the accuracy of the predictions made by each source
distribution.

Take a source distribution, fit the source coefficients and then use them to
predict data on the grid points where the \emph{target grid} is defined.
Define prediction error as the difference between the predicted values and the
\emph{target grid}.

Each source distribution has parameters that need to be specified before
fitting its coefficients.
For example, the \emph{grid of sources} needs the depth at which the sources
will be located.
The damping parameter used on the fitting process must also be specified
beforehand.
These parameters play an important role on the accuracy of the prediction.
We compute several predictions made by the same source distribution, but with
different values for its parameters.
Then we score each interpolation by computing the R$^2$ between each prediction
and the target grid.
We keep the best prediction, i.e.\ the one that has the highest R$^2$ score.

@@

The synthetic airborne survey was based upon the Great Britain aeromagnetic
data, reproduced with the permission of the British Geological Survey
$\textcopyright$UKRI\@.
All rights Reserved.

>>>>

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source bellow data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}

@@

Each source distribution from Table~\ref{tab:source-distributions} needs
certain parameters in order to build the set of point sources.
The prediction capabilities of the source distribution depends on the choice of
these parameters.
For example, locating the sources beneath the data points at constant depth
needs the definition of the \emph{depth} parameter.
If the sources are set too close to the data points, the source distribution
it's very likely to overfit the data: the measured field will be recovered, but
the predictions on unobserved locations will be very inaccurate.
Another parameter that plays an important role on the predictive capabilities
of the sources is the damping parameter.
On real world scenarios, choosing the values of the parameters is a challenging
task: it's not easy to determine the accuracy of the predictions without
knowing the true value of the field on unobserved locations.
This problem can be solved through cross-validation.
When working with a synthetic model, the situation is different: we can compute
the true values of harmonic field generated by the synthetic model on any
point.
Therefore, interpolating the observed data on the same points of the
\emph{target} grid and then scoring the prediction against the true values of
the \emph{target} grid constitutes an objective way to measure the predictive
accuracy of the source distribution.

For each source distribution we proposed different values for each parameter
(including the damping) and combined them into several parameters sets.
For each parameter set we build the sources and fit their coefficients through
least-squares.
Then the sources are used to predict the field on the same points of the
\emph{target} grid and finally we compute the coefficient of determination
(R$^2$ score) between the prediction and the true values of the \emph{target}
grid.
We can therefore obtain the \emph{best prediction} generated by each source
distribution as the one that achieves the highest score.

@@

The synthetic airborne survey was based upon the Great Britain aeromagnetic
data, reproduced with the permission of the British Geological Survey
$\textcopyright$UKRI\@.
All rights reserved.
